### 2018-08-31 scripts/02-metrics/01-metric_characterisation/README.Rmd
update readmes with github_markdown_nested format
fix completely sensible error for when dynbenchmark is not imported in readmes

---
output: 
  github_document:
    pandoc_args: --atx-headers
---

@@

```{r include=FALSE}
library(dynbenchmark)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
```

@@

```{r, results = "asis"}
render_scripts_documentation()
```

The results of this experiment are available [here](`r link_to_results()`)

>>>>

---
output: dynbenchmark::github_markdown_nested
---

@@

@@

```{r}
dynbenchmark::render_scripts_documentation()
```

The results of this experiment are available [here](`r dynbenchmark::link_to_results()`)
